If you see something, then say something to others: Complex contagions and the socially-contingent correction of misinformation

### 2018-02-17 manuscript_1.0.tex
more tweak on network topology
- Probably settle on this ones...
- Also updates on draft

% declare documents and packages
\documentclass[man, 12pt, a4paper, noextraspace]{apa6}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[american]{babel}
\usepackage{csquotes}
\usepackage{amsmath}
\usepackage{microtype}
\usepackage{graphicx}
\usepackage{url}
\usepackage{times}
\renewcommand{\footnotesize}{\normalsize} % use 12pt for footnotes
\usepackage[doublespacing]{setspace} % single space for footnotes
% this command put all footnotes to endnote at the end of the paper
\usepackage{endnotes}
\let\footnote\endnote

@@

\note{Word count: 4431 words \\ %\quickwordcount \\
    Draft date: \today \\
      \addvspace{.25in} 
      \textbf{Draft in progress. Please do not cite without permission.} \\
      Please direct any questions and inquiries to \href{mailto:hyunjin.song@univie.ac.at}{hyunjin.song@univie.ac.at}}

@@

    In contrast, there are reasons to believe why the effectiveness of fact-checking and corrective messages would be different from that of a simple contagion of misinformation. An adoption of a new perspective that contradicts with one's priors (such as an adoption of counter-attitudinal fact-checking messages) is likely to be, in \citeauthor{centola2007complex}'s (\citeyear{centola2007complex}) term, a \enquote{complex contagion} where it requires \emph{exposure to multiple sources}, rather than \emph{multiple number of exposures}, endorsing such message in order to be accepted and further spread into a given network. This is because many political attitudes and subsequent actions (such as politically motivated misperceptions) are likely to be deeply rooted in one’s social identities and values, therefore changes in one's political beliefs and attitudes require multiple sources of affirmation and reinforcement from multiple \emph{contacts} compared to simple contagion cases \parencite[e.g.,][]{gonzalez2011dynamics, larson2016social, siegel2009social}.

    Moreover, such complex contagion dynamics surrounding correction messages are also likely to be dependent upon the attitudinal composition of one's local network. For the case of a adoption of fact-checking and corrective messages, the number of one's neighbors who are \emph{not} activated (e.g., those who still \emph{endorse} false belief based on misinformation) tend to discourages their neighbors to adopt a correction, whereas the number of one's neighbors who are already activated (e.g., those who do not believe misinformation anymore) would increase one's susceptibility to adopt the correction given exposure to such correction \parencites[i.e., a \enquote{\emph{contested}} contagion:][]{centola2007complex}[also see][]{friedkin2001norm}. Indeed, many social contagions are often perceived to be lack of credibility and legitimacy until adopted by one's neighbors, therefore relative distribution of one's neighbors (in terms of supporters vs. opponents of the adoption) critically influence one's decision to adopt a controversial innovation \parencite{larson2016social, gonzalez2011dynamics, friedkin2001norm}. This further means that locally-defined social dynamics may drive specific adoption behaviors of counter-attitudinal information, and consequently, such process would non-trivially interact with a structure and its attitudinal composition of a given network \parencite[e.g.,][]{friedkin2001norm}. Indeed, there exits a considerable support for this perspective, such that different network topologies \parencite[][]{Centola2010Sience, siegel2009social} or attitudinal makeup of social networks\footnote{  Here, we use the term \enquote{attitudinal composition} to denote a relative distribution of supporters vs. opponents regarding a given attitude or a behavior being spread in a network.} \parencite[][]{levitan2008resistance, larson2016social, gonzalez2011dynamics} may produce different attitudinal and behavioral consequences for social influence. This further implies that some network structures are more prone to generating cascades and adoptions than others.

@@

  All in all, prior empirical evidence and theoretical perspectives convincingly suggest that a \emph{simple} contagion of misinformation and a \emph{complex} contagion of corrective messages would exhibit different properties for population-level propagation dynamics. Structurally weak, but bridging ties such as distant contacts in social networks may provide sufficient means for a simple (mis)information -- much like communicable disease -- to be spread, while ideologically-driven directionally motivated reasoning may provide sufficient psychological grounds for partisans to easily adopt and believe such misinformation. In contrast, an adoption of corrective message -- similar to controversial innovations -- requires independent and multiple reinforcements from many social contacts due to its counter-attitudinal and \enquote{contested} nature, critically dependent upon a structure of network and its attitudinal composition \parencite{centola2007complex, Centola2010Sience, gonzalez2011dynamics}. Aforementioned perspectives therefore undoubtedly point to the possibility that adoptions of fact-checking messages are likely to be highly socially-contingent, and under certain cases, a social correction would be much more effective than an isolated correction message as typically have been considered in previous experiment contexts \parencite[e.g.,][]{nyhan2010corrections,garrett2013undermining}.

@@

    This structure has traditionally been known for information to be spread globally through such hubs \parencite[e.g.,][]{Bakshy_2012}, following \citeauthor{granovetter1977strength}'s (\citeyear{granovetter1977strength}) seminal account of strength of weak ties. However, emerging evidence suggests that such a small-world structure may hinder a given diffusion process to globally saturate the network, since such hubs can serve as a \enquote{bottleneck} of a contagion process, therefore diffusions are stay localized and compartmentalized \parencite[e.g.,][]{banos2013diffusion, centola2007complex}. Similarly, while the existence of tightly-knit neighborhoods in a typical small-world network supports a complex-type behavioral propagation \parencite[i.e., an innovation that runs counter to prevalent norms and values:][]{Centola2010Sience}, the existence of hubs may not favor complex contagion to be globally propagated into a given network. This is due to the fact that such hubs require a much higher number of active neighbors to meet the threshold of adopting a controversial innovation (i.e., complex contagions), and even if such hubs are activated, they alone cannot further activate their immediate neighbors to adopt such  innovations in the absence of other local nodes that provide multiple independent reinforcements \parencite{Centola2007449}. Therefore, whether topological properties of a given network actually hinder or facilitate a contagion process may critically dependent upon specific thresholds values for complex contagions and its interaction with the structure of network \parencite[e.g.,][]{Centola2007449}, which is often hard to be tractable empirically.

    Moreover, especially for the case of misinformation and its corrections, a simple contagion (of misinformation) and a complex contagion (of correction messages) may simultaneously affect a local-level attitudinal composition of one's neighbors \parencite[i.e., those who endorse and believe misinformation vs. those who do not: e.g.,][]{campbell2013complex}. Last but not least, all of aforementioned factors are endogenously determined through prior states of networks over time in evolving dynamic network. As a consequence, a proper identification regarding the exact impacts of its attitudinal composition and structural properties of an given network often necessitates systematic comparisons between the observed network and a number of plausible counterfactuals. Doing so further requires (a) the ability to compared different thresholds values for complex contagions, and (b) the ability to independently manipulate topological structures of a social network \parencite[e.g.,][]{Centola2010Sience, Centola2007449}. For this reason, a rigorous empirical test of such factors is often practically impossible for observational studies despite its scientific and practical importance.

@@

  Adopting a well-known class of an epidemic model of virus infection and recovery, this study used stochastic network-based mathematical models to simulate contagion dynamics of misinformation and its corrections. More detailed methods, including model parameterization, simulation, and more detailed analyses of simulation model results, are provided in the supplementary appendix. Behavioral parameters governing the network structure and misinformation propagation dynamics were estimated from several best-available existing sources of empirical data. Although these data sources were not specifically designed for obtaining the impact of (mis)information diffusion dynamics but rather conveniently chosen, it nevertheless provides reasonable starting point for formally model more realistic network structures, on which we later further parameterizing the assumptions and mechanisms postulated in the previous discussions of complex diffusion dynamics. All simulation models were based on the \emph{EpiModel} R software package.

    Utilizing simulation-based approach in modeling (mis)information propagation is not entirely new (CITE HERE). Yet prior studies have typically relied on a series of deterministic compartmental models, where diffusion dynamics were derived by differential equations representing analytic epidemic systems (CITE HERE). While they offer valuable insights of how information spread in a given system, they do not explicitly represent contact phenomena in a network, therefore somewhat limited in realistically representing the evolving dynamic networks on which information and behaviors are spread conditional on the network structure. Our approach was to use exponential random graph models, or ERGM, to simulate a series of dynamically evolving networks of different topological properties (see also below section XXX for a more detail). The ERGM framework is now regarded the most versatile yet flexible method for identifying how a given network is formed and evolves based on the underlying generative principles, and for simulation context, offers a convenient yet powerful tool for independently manipulating topological structures of a network based on such generative mechanisms. In our present application, we therefore simulated a baseline model (based on available empirical evidence) and several counterfactual models (that differ in some key parameters) of network evolution models, and further submit them to different stochastic models of misinformation propagations vs. corrective message adoptions. Our focus here is therefore on the role of varying level of attitudinal homophily as a driving force of network evolutions, and how attitudinal compositions of one's local networks (as end-results of attitudinal homophily) interactively influence simple vs. complex contagion dynamics at population level in conjunction with network topologies.

    Therefore, our approach differ from a number of prior studies that have used similar simulation-based approach in three critical aspects: (a) instead of relying on purely hypothetical scenarios and parameter values, we augment our model by supplying more realistic parameter values based on existing empirical evidence; (b) our model explicitly takes into account the stochastic nature of network evolution and its endogenous influence over time; and finally, (c) we explicitly model how attitudinal compositions of one's immediate neighbors and local-level contagion dynamics (i.e., simple vs. complex contagions) interact to yield propagation dynamics at the population level. Arguably, this approach obviously still greatly simplifies the complexity of the real world. However, in doing so, it provides an analytical tool for identifying the effects topologies and attitudinal compositions of a network, and the resulting implications for the simple vs. complex diffusion dynamics of misinformation and corrections in a typical social network.

\printbibliography
\newpage
\begingroup
\parindent 0pt
\parskip 1ex
\def\enotesize{\normalsize}
\theendnotes
\endgroup
\end{document}

>>>>

% declare documents and packages
\documentclass[man, 12pt, a4paper, noextraspace]{apa6}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[american]{babel}
\usepackage{csquotes}
\usepackage{amsmath}
\usepackage{microtype}
\usepackage{caption}
\usepackage{subcaption}

\usepackage{graphicx}
\usepackage{url}
\usepackage{times}
\renewcommand{\footnotesize}{\small} % use 11pt for footnotes
\usepackage[doublespacing]{setspace} % single space for footnotes
\setlength{\skip\footins}{1.5pc plus 1pt} % some more space between footnote and main body
% this command put all footnotes to endnote at the end of the paper
%\usepackage{endnotes}
%\let\footnote\endnote

@@

\note{Word count: 5339 words \\ %\quickwordcount \\
    Draft date: \today \\
      \addvspace{.25in} 
      \textbf{Draft in progress. Please do not cite without permission.} \\
      Please direct any questions and inquiries to \href{mailto:hyunjin.song@univie.ac.at}{hyunjin.song@univie.ac.at}}

@@

    In contrast, there are reasons to believe why the effectiveness of fact-checking and corrective messages would be different from that of a simple contagion of misinformation. An adoption of a new perspective that contradicts with one's priors (such as an adoption of counter-attitudinal fact-checking messages) is likely to be, in \citeauthor{centola2007complex}'s (\citeyear{centola2007complex}) term, a \enquote{complex contagion} where it requires \emph{exposure to multiple sources}, rather than \emph{multiple number of exposures}, endorsing such message in order to be accepted and further spread into a given network. This is because many political attitudes and subsequent actions (such as politically motivated misperceptions) are likely to be deeply rooted in one’s social identities and values, therefore changes in one's political beliefs and attitudes require multiple sources of affirmation and reinforcement from multiple \emph{contacts} compared to simple contagion cases \parencite[e.g.,][]{gonzalez2017decoding, larson2016social, siegel2009social}.

    Moreover, such complex contagion dynamics surrounding correction messages are also likely to be dependent upon the attitudinal composition of one's local network. For the case of a adoption of fact-checking and corrective messages, the number of one's neighbors who are \emph{not} activated (e.g., those who still \emph{endorse} false belief based on misinformation) tend to discourages their neighbors to adopt a correction, whereas the number of one's neighbors who are already activated (e.g., those who do not believe misinformation anymore) would increase one's susceptibility to adopt the correction given exposure to such correction \parencites[i.e., a \enquote{\emph{contested}} contagion:][]{centola2007complex}[also see][]{friedkin2001norm}. Indeed, many social contagions are often perceived to be lack of credibility and legitimacy until adopted by one's neighbors, therefore relative distribution of one's neighbors (in terms of supporters vs. opponents of the adoption) critically influence one's decision to adopt a controversial innovation \parencite{larson2016social, gonzalez2017decoding, friedkin2001norm}. This further means that locally-defined social dynamics may drive specific adoption behaviors of counter-attitudinal information, and consequently, such process would non-trivially interact with a structure and its attitudinal composition of a given network \parencite[e.g.,][]{friedkin2001norm}. Indeed, there exits a considerable support for this perspective, such that different network topologies \parencite[][]{Centola2010Sience, siegel2009social} or attitudinal makeup of social networks\footnote{  Here, we use the term \enquote{attitudinal composition} to denote a relative distribution of supporters vs. opponents regarding a given attitude or a behavior being spread in a network.} \parencite[][]{levitan2008resistance, larson2016social, gonzalez2017decoding} may produce different attitudinal and behavioral consequences for social influence. This further implies that some network structures are more prone to generating cascades and adoptions than others.

@@

  All in all, prior empirical evidence and theoretical perspectives convincingly suggest that a \emph{simple} contagion of misinformation and a \emph{complex} contagion of corrective messages would exhibit different properties for population-level propagation dynamics. Structurally weak, but bridging ties such as distant contacts in social networks may provide sufficient means for a simple (mis)information -- much like communicable disease -- to be spread, while ideologically-driven directionally motivated reasoning may provide sufficient psychological grounds for partisans to easily adopt and believe such misinformation. In contrast, an adoption of corrective message -- similar to controversial innovations -- requires independent and multiple reinforcements from many social contacts due to its counter-attitudinal and \enquote{contested} nature, critically dependent upon a structure of network and its attitudinal composition \parencite{centola2007complex, Centola2010Sience, gonzalez2017decoding}. Aforementioned perspectives therefore undoubtedly point to the possibility that adoptions of fact-checking messages are likely to be highly socially-contingent, and under certain cases, a social correction would be much more effective than an isolated correction message as typically have been considered in previous experiment contexts \parencite[e.g.,][]{nyhan2010corrections,garrett2013undermining}.

@@

    This structure has traditionally been known for information to be spread globally through such hubs \parencite[e.g.,][]{Bakshy_2012}, following \citeauthor{granovetter1977strength}'s (\citeyear{granovetter1977strength}) seminal account of strength of weak ties. However, emerging evidence suggests that such a small-world structure may hinder a given diffusion process to globally saturate the network, since such hubs can serve as a \enquote{bottleneck} of a contagion process, therefore diffusions are stay localized and compartmentalized \parencite[e.g.,][]{banos2013diffusion, centola2007complex, zhao2010weak}. Similarly, while the existence of tightly-knit neighborhoods in a typical small-world network supports a complex-type behavioral propagation \parencite[i.e., an innovation that runs counter to prevalent norms and values:][]{Centola2010Sience}, the existence of hubs may not favor complex contagion to be globally propagated into a given network. This is due to the fact that such hubs require a much higher number of active neighbors to meet the threshold of adopting a controversial innovation (i.e., complex contagions), and even if such hubs are activated, they alone cannot further activate their immediate neighbors to adopt such  innovations in the absence of other local nodes that provide multiple independent reinforcements \parencite{Centola2007449, zhao2010weak, gonzalez2017decoding}. Therefore, whether topological properties of a given network actually hinder or facilitate a contagion process may critically dependent upon specific thresholds values for complex contagions and its interaction with the structure of network \parencite[e.g.,][]{Centola2007449}, which is often hard to be tractable empirically.

    Moreover, especially for the case of misinformation and its corrections, a simple contagion (of misinformation) and a complex contagion (of correction messages) may simultaneously affect a local-level attitudinal composition of one's neighbors \parencite[i.e., those who endorse and believe misinformation vs. those who do not: e.g.,][]{campbell2013complex}. Last but not least, all of aforementioned factors are endogenously determined through prior states of networks over time in evolving dynamic network. As a consequence, a proper identification regarding the exact impacts of its attitudinal composition and structural properties of an given network often necessitates systematic comparisons between the observed network and a number of plausible counterfactuals. Doing so further requires (a) the ability to compared different thresholds values for complex contagions, and (b) the ability to independently manipulate topological structures of a social network \parencite[e.g.,][]{Centola2010Sience, Centola2007449, gonzalez2017decoding}. For this reason, a rigorous empirical test of such factors is often practically impossible for observational studies despite its scientific and practical importance.

@@

  Adopting a well-known class of an epidemic model of virus infection and recovery, this study used stochastic network-based mathematical models to simulate contagion dynamics of misinformation and its corrections. More detailed methods, including model parameterization, simulation, and more detailed analyses of simulation model results, are provided in the supplementary appendix. Behavioral parameters governing the network structure and misinformation propagation dynamics were estimated from several best-available existing nationwide representative surveys concerning citizen's social network \parencite[American National Election Study 2008–2009 Panel Survey:][]{ANES2009} and exposure to fake news during 2016 presidential election \parencite{pewfakenews}. Although these data sources were not specifically designed for obtaining the impact of (mis)information diffusion dynamics within a social network but rather conveniently chosen,\footnote{  It should be acknowledged that those sources of data is suboptimal in number of regards: (a) social network data is confined to cross-sectional, egocentric network data, and (b) they do not come from the identical data generating process covering the same periods of observations (e.g., networks recoded in 2009 has little or no bearing for fake news exposure in 2016). However, research indicates the structural compositions of citizens' core discussion network are reasonably stable over time, albeit actual responses in typical surveys are subject to a number of survey-context related factors \parencite{byungkyu2017important} or changes in one's life contexts \parencite{small2015stable}. Also, since most of the prior applications concerning fake news and misinformation from observational studies typically look at representative samples, we intentionally have chosen those data since these types of data are more commonly used in the social sciences, which provide best-available up-to-date relevant information for the current application. See also \textit{A Stochastic Dynamic Model of Networks} section below and supplemental appendix for a detail.} it nevertheless provides reasonable starting point for formally model more realistic network structures, on which we later further parameterizing the assumptions and mechanisms postulated in the previous discussions of complex diffusion dynamics. All simulation models were based on the \emph{EpiModel} R software package \parencite{epimodel}.

    Utilizing simulation-based approach in modeling (mis)information propagation is not entirely new \parencite[e.g.,][]{tambuscio2015fact, jin2013epidemiological, acemoglu2010spread, zhao2010weak}. Yet these studies have typically relied on a series of deterministic compartmental models, where diffusion dynamics were derived by differential equations representing analytic epidemic systems \parencite[e.g., see][]{zhao2010weak}. While they offer valuable insights of how information spread in a given system, they do not explicitly represent contact phenomena in a network, therefore somewhat limited in realistically representing the evolving dynamic networks on which information and behaviors are spread conditional on the network structure. Our approach was to use an exponential random graph model, or ERGM framework \parencite{robins2007introduction, morris2008specification}, to simulate a series of dynamically evolving networks of different topological properties (see also below section XXX for a more detail). The ERGM framework is now regarded the most versatile yet flexible method for identifying how a given network is formed and evolves based on the underlying generative principles \parencite{cranmer2017navigating, robins2007introduction}, and for a simulation context, it offers a convenient yet powerful tool for independently manipulating topological structures of a network based on such generative mechanisms by a researcher's choice \parencite{morris2008specification, leifeld2017temporal}. In our present application, we therefore simulated a baseline model (based on available empirical evidence) and several counterfactual models (that differ in some key parameters) of network evolution models, and further submit them to different stochastic models of misinformation propagations vs. corrective message adoptions. Our focus here is therefore on the role of varying level of attitudinal homophily as a driving force of network evolutions, and how attitudinal compositions of one's local networks (as end-results of attitudinal homophily) interactively influence simple vs. complex contagion dynamics at population level in conjunction with network topologies.

    Therefore, our approach differs from prior studies that have used similar simulation-based approaches in three critical aspects: (a) instead of relying on purely hypothetical scenarios and parameter values, we augment our model by supplying more realistic parameter values based on existing empirical evidence; (b) our model explicitly takes into account the stochastic nature of network evolution and its endogenous influence over time; and finally, (c) we explicitly model how attitudinal compositions of one's immediate neighbors and local-level contagion dynamics (i.e., simple vs. complex contagions) interact to yield propagation dynamics at the population level. Arguably, this approach obviously still greatly simplifies the complexity of the real world. However, in doing so, it provides an analytical tool for identifying the effects topologies and attitudinal compositions of a network, and the resulting implications for the simple vs. complex diffusion dynamics of misinformation and corrections in a typical social network.

\subsection{A Stochastic Dynamic Model of Networks}

  In order to explore role of network topologies in diffusion dynamic in evolving networks, we require to explicitly specify a network structure and how such structure evolves over time according to some underlying generative principles. To this end, we first model formation and dissolution of citizens' political discussion ties over time (through which misinformation and corrections are communicated) using separable temporal ERGMs (STERGMs), using \enquote{summary statistics} drawn from egocentric network samples \parencite{krivitsky2017inference}. That is, we estimate and simulate \emph{complete networks} that consistently reproduce observed properties of egocentrically sampled information from 2009 ANES data.\footnote{ Of course, this approach requires certain assumptions in order to define a model that represents a distribution of networks that are centered on the observed properties. See \citeauthor{krivitsky2017inference} (\citeyear{krivitsky2017inference}) for a detailed discussion of this class of models and their properties.} Those observed properties, or summary target statistics, include: density (i.e., average number of discussion partners, or \enquote{alters}), average expected number of degrees among Democrats and Republicans excluding Independents (i.e., main effect of partisanship), the extent of partisan homophily (i.e., interaction between ego and alter partisanship), and number of people who posses multiple contacts (i.e., degree distributions).\footnote{  In 2009 ANES panel, there are a total of 1258 self-identified Democrats and 1142 self-identified Republicans (including respective party leaners), excluding 336 Independents. Those 2400 partisans (i.e., Democrats plus Republicans) have on average 1.975 discussion partners. Since in 2009 ANES respondents theoretically name up to three alters, this translate into egonetwork density of 0.66 (=1.975/3). For the main effect of partisanship, the marginal distribution of number of named alters by egos did not differ by partisanship, meaning that the expected mean degree for each partisan group is proportional to observed density and the size of each group. For political homophily, data indicate that 23\% of reported discussion ties exist across Democrats and Republicans. For degree distribution statistic, we supply a range of plausible yet arbitrary values since 2009 ANES does not have summary network size measure. See supplemental appendix for a detail.} Based on those information, we establish our (a) baseline small-world with political homophily network model, which consist of 2400 nodes that comprised of 1258 Democrats and 1142 Republicans. In this model, we set approximately 70\% of all exiting ties to be politically homophilous based on observed level of political homogeneity in ANES egocentric networks. We also specify a differential relationship dissolution conditional on partisan homophily of a tie \parencite[e.g., selective "unfriending":][]{noel2011unfriending}, such that any tie within the same partisan group is expected to last longer approximately twice than cross-partisan discussion ties. 
    In addition, in order to facilitate a robust comparison of different network typologies, we additionally specify several counterfactual models of network structure: (b) Erdős–Rényi random network conditional on observed density, (c) a chain network where all nodes have no more than two connections at the same time,\footnote{  This is done by first simulating a lattice network (e.g., all nodes have exactly the same number of degrees), but due to the stochastic nature of evolving network in which ties are randomly created and dissolved, the resulting network may not have the uniform degree distribution than it would have been under strict lattice network.} and (d) a small-world network \textit{absent of partisan homophily} in tie formation and tie dissolution model. Below Figure \ref{fig:Figure1} shows the simulated cross-sectional networks from each of the network topologies, and Table \ref{tab:Table1} reports some key descriptive statistics from each of the networks.
\begin{center} -- Table \ref{tab:Table1} and Figure \ref{fig:Figure1} about here -- \end{center}

% Table 1.
\begin{table}[!htbp] \centering 
  \caption{\\ Descriptive Statistics of Cross-sectional Networks from Simulated Network Structures} 
  \label{tab:Table1} 
\begin{tabular}{@{\extracolsep{5pt}} ccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \textbf{E-R} & \textbf{Chain} &  \textbf{SW No-Homophily} & \textbf{SW Homophily} \\ 
\hline \\[-1.8ex] 
Density & 0.000272 & 0.000275 & 0.000274 & 0.000268 \\ 
Mean degree & 1.305 & 1.318 & 1.315 & 1.287 \\ 
Max degree & 10.0 & 4.0 & 10.0 & 10.0 \\ 
Clustering coefficients & 0.0 & 0.0 & 0.02 & 0.01 \\ 
Mean distance & 3.0 & 2.4 & 3.6 & 3.4 \\ 
Homophilous ties & 50.7\% & 47.3\% & 51.2\% & 74.6\% \\ 
Heterophilous ties & 49.3\% & 52.7\% & 48.8\% & 25.4\% \\ 
\hline \\[-1.8ex]  
\end{tabular} 
\begin{tablenotes}[para,flushleft]
\small \vspace{0.15in}
\textbf{Note:} E-R: Erdos Renyi random network. Chain: Chain network. SW No-Homophily: Small-world network absent of homophily. SW Homophily: Small-world network with partisan homophily. 
\end{tablenotes}
\end{table}

% Figure 1: Plots of static (cross-sectional) networks from simulations    
\begin{figure}
\captionsetup[figure]{labelfont={bf,it}}
\captionsetup[subfigure]{labelfont=bf,textfont=normalfont,singlelinecheck=on}
    \centering
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[trim={2cm 2cm 2cm 2cm}, clip, width=\linewidth]{draft/network_plots1.pdf} 
        \caption{Erdos-Renyi random network}
        \label{fig1:random}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[trim={2cm 2cm 2cm 2cm}, clip, width=\linewidth]{draft/network_plots2.pdf} 
        \caption{Chain network} \label{fig1:tree}
    \end{subfigure}

    \vspace{1cm}
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[trim={2cm 2cm 2cm 2cm}, clip, width=\linewidth]{draft/network_plots3.pdf} 
        \caption{Small-world network absent homophily} \label{fig1:nohomophily}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[trim={2cm 2cm 2cm 2cm}, clip, width=\linewidth]{draft/network_plots4.pdf} 
        \caption{Baseline small-world network} \label{fig1:smallworld}
    \end{subfigure}

    \vspace{1cm}
    \captionsetup{format=hang}
    \caption{A cross-sectional view of simulated networks from different network topologies. Colored nodes represent nodes that have at least one connection with their neighbor (Red = Republicans, Blue = Democrats) while isolates at given time point was suppressed in visualization. A Erdos-Renyi (ER) random network (a) assumes a homogeneous probability of creating and dropping ties across all nodes conditional on observed density. A chain-like network (b) has more longer chains than the ER random network while lacks triangle-like structure due to constrains on degrees (less than three). While two small-world network has more star-like structure than others, our baseline small-world network (d) is more homophilous than competing specification in (c), as can be seen in Table \ref{tab:Table1}.} \label{fig:Figure1}
\end{figure}

\subsection{Misinformation Transmission and Progression}

\subsection{Corrective Message Exposure and a Recovery from Misperception}

\printbibliography
%\newpage
%\begingroup
%\parindent 0pt
%\parskip 1ex
%\def\enotesize{\normalsize}
%\theendnotes
%\endgroup
\end{document}
